SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-06 frontrunning/Latex/sections/paper.tex
[frontrunning] Fix affiliate + comments about cryptokitties
Add notes from meeting on Feb 5th
[frontrunning] add erc20 approve attack

Given the purpose of this entire paper is systemizing the existing literature, we do not re-enumerate the literature here. However, we note two things. First, we are not aware of any other systematic study of this issue. Second, front-running is related to two well-studied concepts: double-spending and rushing adversaries.

@@

Double-spending attacks in Bitcoin are related to front-running~\cite{bamert2013have,karame2012double}. In this attack, a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed. The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners or artifacts of the network topology to have the second transaction confirmed instead of the first. This can be considered a form of \textsf{self-front-running}.

In the cryptographic literature, front-running attacks are modeled by allowing a `rushing' adversary to interact with the protocol. In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running. See \eg Bitcoin backbone~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.

@@

As seen in traditional financial markets, one method to manipulate the spot price of an asset, is to flood the market with orders and cancel them when there are filling orders (``taker's griefing''~\cite{consesnsys0xReview2017}). Placing an order in a partially centralized exchange is free, but to prevent taker's griefing attacks, the user needs to send an Ethereum transaction to cancel each of his orders. Cancelling orders is most important when prices change faster than order execution. In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled (this is known as \textit{cancellation grief}). This attack follows the (asymmetric) insertion template and is illustrated in Figure~\ref{fig:MinerFrontrunning}.

@@

@@

>>>>

Given the purpose of this entire paper is systemizing the existing literature, we do not re-enumerate the literature here. However, we note two things. First, we are not aware of any other systematic study of this issue. Second, front-running is related to two well-studied concepts: double-spending and rushing adversaries~\cite{kosba2016hawk}.

@@

Double-spending attacks in Bitcoin are related to front-running~\cite{bamert2013have,karame2012double}. In this attack, a user broadcasts a transaction and is able to obtain some off-blockchain good or service before the transaction has actually been (fully) confirmed. The user can then broadcast a competing transaction that sends the same unspent coins to herself, perhaps using higher transaction fees, arrangements with miners or artifacts of the network topology to have the second transaction confirmed instead of the first. This can be considered a form of \textsf{self-front-running}.
In the cryptographic literature, front-running attacks are modeled by allowing a so called `rushing' adversary to interact with the protocol~\cite{beaver1992cryptographic}. In particular, ideal functionalities of blockchains (such as those used in simulation-based proofs) need to capture this adversarial capability, assuming the real blockchain does not address front-running. See \eg Bitcoin backbone~\cite{garay2015bitcoin} and Hawk~\cite{kosba2016hawk}.

@@

As seen in traditional financial markets, one method to manipulate the spot price of an asset, is to flood the market with orders and cancel them when there are filling orders (``taker's griefing''~\cite{consesnsys0xReview2017}). Placing an order in a partially centralized exchange is free, but to prevent taker's griefing attacks, the user needs to send an Ethereum transaction to cancel each of his orders. Cancelling orders is most important when prices change faster than order execution. In this case, when an adversarial actor sees a pending cancellation transaction, he sends a fill order transaction with higher gasPrice to get in front of the cancellation order and take the order before it is canceled (this is known as \textit{cancellation grief}). This attack follows the (asymmetric) insertion template and is illustrated in Figure~\ref{fig:MinerFrontrunning}. %0x has also added an option to cancel all orders through a batch cancellation mechanism to mitigate this issue.

@@

% Shayan TODO:
% remove most of the text above and replace it with references: https://hackernoon.com/how-we-made-100k-trading-cryptokitties-2d69aebe715b
% disuss the application specific front-running, which is with giveBirth() function and front-running other calls
% https://medium.com/block-science/exploring-cryptokitties-part-2-the-cryptomidwives-a0df37eb35a6
% maybe: https://blog.kleros.io/generalized-ethereum-frontrunners-an-implementation-and-a-cheat/

@@

%Shayan -> Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
Another example is in the design of ERC20 standard~\cite{erc20}, is on the allowance functionality. \textit{approve()} function in the specification allows a second entity to be able to spend N tokens from the sender's balance. In order to change the allowance, sender must set the new allowance value to\textit{approve()}. An attacker, using the insertion attack, could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}. Later on solutions such as \textit{decreaseApproval() / increaseApproval()} was added instead of replacing the value.
